An Authoritative Adventure

### 2020-09-13 article.tex
Added example usage of new theme color control option
Added the "letteredarea" example and tweaked the alternate map layout section

@@

\section{Alternate Map Region Styles}
Published modules sometimes use plain numbers for locations, sometimes they
prefix a character to the front of the numbers. The following options can be
used to display in these forms:

@@

\numberedsubarea{Entry}
\numberedsubarea{Trap}
\numberedsubarea{Fight}
\numberedsubarea{Exit}

\prefixedarea{Ace Dungeon}{A}
Areas in the Ace Dungeon are prefixed with `\prefixedareaprefix'.
This is done using the following commands:

\begin{verbatim}
\prefixedarea{Ace Dungeon}{A}
\prefixedsubarea{Entry}
\prefixedsubarea{Exit}
\end{verbatim}

\prefixedsubarea{Entry}
\prefixedsubarea{Exit}

\prefixedarea{The Fantastic Zoo}{Z}
Areas in the Fantastic Zoo are prefixed with `\prefixedareaprefix'.

\prefixedsubarea{Entry}
\prefixedsubarea{Exit}

>>>>

% The settings below are an example of how to modify all of the theme colors.
% Note that the paper (\SetPaperImage) and footerscroll.pdf will probably need
% to be modified for any % major color scheme change. The values below are
% thematic for a sourcebook like GoS.
\definecolor {mytheme}      {HTML} {DCF1E5} %
\definecolor {mysidebar}    {HTML} {E9F5F5} %
\definecolor {myreadaloud}  {HTML} {DCF1E5} %
\definecolor {myreadaloudborder}  {HTML} {8AA7A2} %
\definecolor {mypagenum}  {HTML} {B5D4CF} %
%\DndSetComplexThemeColor[mytheme][mysidebar][myreadaloud][myreadaloudborder][titlered][titlegold][mypagenum]

@@

\section{Alternate Map Region Styles}
Published modules sometimes use plain numbers for locations, sometimes plain
letters, and sometimes they prefix a character to the front of the numbers.
The following options can be used to display in these forms:

@@

These commands yield the following results:
\numberedsubarea{Entry}
\numberedsubarea{Trap}
\numberedsubarea{Fight}
\numberedsubarea{Exit}

\letteredarea{Lettered Dungeon}
Areas in the Lettered Dungeon are labelled with sequential characters
(A, B, C, etc). This is done using the following commands:

\begin{verbatim}
\letteredarea{Lettered Dungeon}
\letteredsubarea{Entry}
\letteredsubarea{Trap}
\letteredsubarea{Fight}
\letteredsubarea{Exit}
\end{verbatim}

These commands yield the following results:
\letteredsubarea{Entry}
\letteredsubarea{Trap}
\letteredsubarea{Fight}
\letteredsubarea{Exit}

\prefixedarea{Prefixed Dungeon}{Z}
Areas in the Prefixed Dungeon have a custom prefix character,
in this case: `\prefixedareaprefix'.
This is done using the following commands:

\begin{verbatim}
\prefixedarea{Prefixed Dungeon}{Z}
\prefixedsubarea{Entry}
\prefixedsubarea{Trap}
\prefixedsubarea{Fight}
\prefixedsubarea{Exit}
\end{verbatim}

These commands yield the following results:
\prefixedsubarea{Entry}
\prefixedsubarea{Trap}
\prefixedsubarea{Fight}
\prefixedsubarea{Exit}
